Fast approximate Bayesian inference for small-area estimation of HIV indicators using the Naomi model

### 2023-06-13 src/docs_paper/paper.Rmd
First shot at an interesting 2D non-Gaussian distribution

```{r aghq, fig.cap="The Gauss-Hermite quadrature nodes $\\z \\in \\mathcal{Q}(2, 3)$ for this two dimensional integral with three nodes per dimension are adapted based on the mean and covariance matrix of the target via the Cholesky decomposition or spectral decompostion of the inverse curvature at the mode."}
mu <- c(1, 1.5)
cov <- matrix(c(2, 1, 1, 1), ncol = 2)

obj <- function(theta) {
  mvtnorm::dmvnorm(theta, mean = mu, sigma = cov)
}

grid <- expand.grid(
  theta1 = seq(-2, 5, length.out = 700),
  theta2 = seq(-2, 5, length.out = 700)
)

ground_truth <- cbind(grid, pdf = apply(grid, 1, obj))

plot0 <- ggplot(ground_truth, aes(x = theta1, y = theta2, z = pdf)) +
  geom_contour(col = "lightgrey") +
  coord_fixed(xlim = c(-2, 4.5), ylim = c(-2, 4.5), ratio = 1) +
  labs(x = "", y = "") +
  theme_minimal() +
  guides(size = FALSE) +
  theme(
    axis.text.x = element_blank(), axis.ticks.x = element_blank(),
    axis.text.y = element_blank(), axis.ticks.y = element_blank()
  )

>>>>

```{r aghq, fig.cap="The Gauss-Hermite quadrature nodes $\\z \\in \\mathcal{Q}(2, 3)$ for this two dimensional integral with three nodes per dimension are adapted based on the mean and covariance matrix of the target via the Cholesky decomposition or spectral decompostion of the inverse curvature at the mode."}
TMB::compile("2d.cpp")
dyn.load(TMB::dynlib("2d"))

obj <- TMB::MakeADFun(data = list(), parameters = list(theta1 = 0, theta2 = 0), DLL = "2d")

grid <- expand.grid(
  theta1 = seq(-5, 5, length.out = 400),
  theta2 = seq(-5, 5, length.out = 400)
)

ground_truth <- cbind(grid, pdf = apply(grid, 1, function(x) exp(-1 * obj$fn(x))))

opt <- nlminb(
  start = obj$par,
  objective = obj$fn,
  gradient = obj$gr,
  control = list(iter.max = 1000, trace = 0)
)

sd_out <- TMB::sdreport(
  obj,
  par.fixed = opt$par,
  getJointPrecision = TRUE
)

mu <- opt$par
cov <- as.matrix(sd_out$cov.fixed)

plot0 <- ggplot(ground_truth, aes(x = theta1, y = theta2, z = pdf)) +
  geom_contour(col = "lightgrey") +
  labs(x = "", y = "") +
  theme_minimal() +
  guides(size = FALSE) +
  theme(
    axis.text.x = element_blank(), axis.ticks.x = element_blank(),
    axis.text.y = element_blank(), axis.ticks.y = element_blank()
  )
